D. Glasner, S. Bagon, and M. Irani, “Super-resolution from a single image,” in Proc. Int. Conf. Computer Vision, 2009, pp. 349–356.
T. Akgun, Y. Altunbasak, and R. M. Mersereau, “Super-resolu- tion reconstruction of hyperspectral images,” IEEE Trans. Image Process., vol. 14, no. 11, pp. 1860–1875, 2005.

J. C.-W. Chan, J. Ma, and F. Canters, “A comparison of superreso- lution reconstruction methods for multi-angle CHRIS/Proba im- ages,” in Proc. SPIE, Image and Signal Processing for Remote Sensing XIV, 710904, vol. 7109, Oct. 1, 2008. doi: 10.1117/12.800256

J. C.-W. Chan, J. Ma, P. Kempeneers, and F. Canters, “Super- resolution enhancement of hyperspectral CHRIS/Proba images with a thin-plate spline nonrigid transform model,” IEEE Trans. Geosci. Remote Sens., vol. 48, no. 6, pp. 2569–2579, 2010.

J. C.-W. Chan, J. Ma, T. Van de Voorde, and F. Canters, “Pre- liminary results of superresolution-enhanced angular hyper- spectral (CHRIS/Proba) images for land-cover classification,” IEEE Geosci. Remote Sens. Lett., vol. 8, no. 6, pp. 1011–1015, 2011.

L. Demarchi, J. C.-W. Chan, J. Ma, and F. Canters, “Mapping impervious surfaces from superresolution enhanced CHRIS/Proba imagery using multiple endmember unmixing,” ISPRS J. Photogramm. Remote Sens., vol. 72, pp. 99–112, Aug. 2012.

S. Qian and G. Chen, “Enhancing spatial resolution of hyper- spectral imagery using sensor’s intrinsic keystone distortion,” IEEE Trans. Geosci. Remote Sens., vol. 50, no. 12, pp. 5033–5048, 2012.

Y. Zhao, J. Yang, Q. Zhang, L. Song, Y. Cheng, and Q. Pan, “Hy- perspectral imagery super-resolution by sparse representation and spectral regularization,” EURASIP J. Adv. Signal Process., vol. 2011, no. 87, 2011.

Y. Zhao, J. Yang, and J. C.-W. Chan, “Hyperspectral imagery super-resolution by spatial–spectral joint nonlocal similarity,” IEEE J. Sel. Topics Appl. Earth Observ. in Remote Sens., vol. 7, no. 6, pp. 2671–2679, 2014.

R. C. Patel and M. V. Joshi, “Super-resolution of hyperspectral images: Use of optimum wavelet filter coefficients and sparsity regularization,” IEEE Trans. Geosci. Remote Sens., vol. 53, no. 4, pp. 1728–1736, 2015.

A. Liu, Y. Liu, J. Gu, Y. Qiao and C. Dong, "Blind Image Super-Resolution: A Survey and Beyond," in IEEE Transactions on Pattern Analysis and Machine Intelligence, 2022, doi: 10.1109/TPAMI.2022.3203009.

J. Li, Q. Yuan, H. Shen, X. Meng and L. Zhang, "Hyperspectral Image Super-Resolution by Spectral Mixture Analysis and Spatial–Spectral Group Sparsity," in IEEE Geoscience and Remote Sensing Letters, vol. 13, no. 9, pp. 1250-1254, Sept. 2016, doi: 10.1109/LGRS.2016.2579661.

Linwei Yue, Huanfeng Shen, Jie Li, Qiangqiang Yuan, Hongyan Zhang, Liangpei Zhang, Image super-resolution: The techniques, applications, and future, Signal Processing, Volume 128, 2016, Pages 389-408, ISSN 0165-1684, https://doi.org/10.1016/j.sigpro.2016.05.002.

Q. Wang, W. Shi, P. M. Atkinson and Q. Wei, "Approximate Area-to-Point Regression Kriging for Fast Hyperspectral Image Sharpening," in IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing, vol. 10, no. 1, pp. 286-295, Jan. 2017, doi: 10.1109/JSTARS.2016.2569480.

https://www.spiedigitallibrary.org/conference-proceedings-of-spie/10799/1079905/Assessing-the-prospects-for-robust-sub-diffraction-limited-super-resolution/10.1117/12.2325158.full